% Thesis Acknowledgements ------------------------------------------------


%\begin{acknowledgementslong} %uncommenting this line, gives a different acknowledgements heading
\begin{acknowledgements}      %this creates the heading for the acknowlegments


This dissertation would not have been possible without the guidance and the help of several individuals who in one way or another contributed and extended their valuable assistance in course of this study.

\vspace{.5cm}
The author would like to thank his supervisor, Dr. Sarat Kumar Patra, for his guidance and support on this research work. The author would also like to acknowledge his co-supervisor, Dr. Kamalakanta Mahapatra for his kind advice and inspiration. 

\vspace{.5cm}
The author would like to thank Board of Research for Fusion Science and Technology (BRFST) and Institute of Plasma Research, Gandhinagar for funding major part of this research. The author would like to extend his gratitude towards Dr. Govindarajan, Mr. J. J. Patel, Mrs. Rachana Rajpal and Mr. Hitesh Patel of Institute of Plasma Research, Gandhinagar, for their contributions to this project. 

\vspace{.5cm}
The author would also like to thank Prof. B. Subudhi, Prof. D. P. Acharya, Prof. P. M. Khillar and Prof. S. Meher for their innovative ideas and review during the entire duration of the project. 

\vspace{.5cm}
The author would also like to acknowledge and appreciate the help from the faculty members especially Prof. S. Hiremath, Prof. A. K. Swain, Prof. M. Okhade and Prof. S. Deshmukh of the department for their continuous encouragement to delve into analytical aspects of this work. The author would be grateful to the support extended by the staff members of the department, specially Mr. P. Oram and Mr. Ishwar during the entire journey.

\vspace{.5cm}
The author would also like to thank his friends, especially Deepak, Umakant, Bodhisattwa, Bhaskar, Chithra, Manas, Varun, Goutam, Sankat, Bibhu, Deepak, Asis and Pramit for their accompaniment. Their enduring effort in proof reading of the thesis is unforgettable. The author would also like to extend his gratitude to his seniors Prashant, Sudheendra, Jagannath, Yogesh, Manab and Dipak. The author would also like to thank his lab partner Satyendra for his extensive support and assistance during the entire period of his doctoral studies.

\vspace{.5cm}
And finally the author would like to thank his family and friends, whose faith and patience had always been the inspiring factor.

\vspace{1cm}
\begin{flushright}
\large Pallab Maji\\
\small\textit{pallab.vsp@gmail.com}
\end{flushright}


\end{acknowledgements}
%\end{acknowledgmentslong}

% ------------------------------------------------------------------------

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "../thesis"
%%% End:
