\chapter{Dissemination of Work}

\section*{Journals}
\begin{enumerate}
    \item P. Maji, S. K. Patra, K. Mahapatra, ``Design of Real-time Reconfigurable Fuzzy Logic Controller with M-FRHC Rule Reduction Technique'', Journal of Intelligence and Fuzzy Systems,  vol. 30, no. 4, pp. 1973-1986, 2016.
    \item P. Maji, S. K. Patra, K. Mahapatra, ``Design and Implementation of Fuzzy Approximation PI Controller with Genetic Algorithm based Fuzzy Parameter Extraction'' Advances in Artificial Intelligence, vol. 2015, Article ID 624638, 7 pages, 2015. doi:10.1155/2015/624638. 
\end{enumerate}

\section*{Conference}
\begin{enumerate}
    \item \textbf{P. Maji}, S. K. Patra, and K. Mahapatra, ``Implementation of FPGA based fuzzy PI approximate control for automatic cruise control system,'' in International Conference on Circuits, Communication, Control and Computing, I4C-2014, IEEE, Bangalore, 2014, pp. 203-206..
	\item \textbf{P. Maji}, B. R. Jammu, S. K. Patra, and K. Mahapatra, ``Design and implementation of online fuzzy logic controller on FPGA,'' 2014 Annual IEEE India Conference (INDICON), Pune, 2014, pp. 1-5.
	\item \textbf{P. Maji}, S. K. Patra, K. Mahapatra, J. Govindarajan, and J. J. Patel, ``Realization of reconfigurable FLC on ADSP-BF537 processor,'' 4th International Conference on Computing, Communications and Networking Technologies, ICCCNT-2013, IEEE, 2013, pp. 1-4.
	\item \textbf{P. Maji}, S. K. Patra, and K. Mahapatra, ``Design of Fuzzy Logic Controller based on TMS320C6713 DSP,'' 12th International Conference on Intelligent System Design and Application, ISDA-2012, IEEE, Kochi, 2012, pp. 635-639.
\end{enumerate}


\section*{Journals: Under Review}
\begin{enumerate}
	\item P. Maji, S. K. Patra, K. Mahapatra, ``Rule Reduction Technique for Generic Fuzzy Logic Systems'' to the journal of Fuzzy Information and Engineering (Elsevier). 
	\item P. Maji, S. K. Patra, K. Mahapatra, ``Generic Fuzzy Logic Controller: Design and Implementation with Vertices based Centroid of Area Defuzzification'' to the International Journal of Computational Intelligence Systems (World Scientific).
\end{enumerate}
